---
output:
  github_document:
    html_preview: false
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Overview

The package `"binomial"` is an [R](http://www.r-project.org/) package that implements functions for calculating probabilities of a Binomial random variable.


* `bin_choose()` Calculates the number of combinations in which *k* successes can occur in *n* trials.
* `bin_probability()` Calculates the probability of gatting *k* successes in *n* trails with *prob* of success.
* `bin_distribution()` Return a data frame with the probability distribution: *sucesses* in the first column, *probability* in the second column.
* `plot()` Method that graphs a barplot to display the probability histogram of a binomial distribution.   
* `bin_cumulative()` Takes two arguments *trials* and *prob* that a binomial random variable object "binvar".
* `plot()` Method to graph the cumulative distribution.
* `print.summary.binvar()` Method to nicely print the contents of an object "summary.binvar"
* `bin_mean()` Calculate the mean (expected value) of a binomial variable
* `bin_variance()` Calculate the variance of a binomial variable.
* `bin_mode()` Calculate the mode of a binomial variable.
* `bin_skewness()` Calculate the skewness of a binomial variable.
* `bin_kurtosis()` Calculate the kurtosis (tailedness) of a binomial variable.


## Motivation

This package has been developed to provide tools for calculating probabilties of binomial random variables.


## Installation

Install the development version from GitHub via the package `"devtools"`:

``` r
# development version from GitHub:
install.packages("devtools") 
# install "binomial" (without vignettes)
devtools::install_github("stat133-sp19/hw-stat133-YuniSatoshi/binomial")
# install "binomial" (with vignettes)
devtools::install_github("stat133-sp19/hw-stat133-YuniSatoshi/binomial", build_vignettes = TRUE)
```

## Usage

```{r}
library(binomial)
library(ggplot2)

# For instance
# the number of combinations in which k = 2 successes can occur in n = 5 trials is
bin_choose(5, 2)
# the probability of getting 2 successes in 5 trials, assuming prob of success = 0.5 is
bin_probability(2, 5, 0.5)
# graph a barplot to display the probability histogram of a binomial distribution   
dis1 <- bin_distribution(5, 0.5) 
plot(dis1)
# return a data frame with both the probability distribution and the cumulative probabilities
bin_cumulative( 5,  0.5)
# graph the cumulative distribution
dis2 <- bin_cumulative(5, 0.5) 
plot(dis2)
# nicely print the content of the object "binvar"
bin1 <- bin_variable(10, 0.3) 
bin1
# print the contents of an object "summary.binvar"
bin1 <- bin_variable(10, 0.3) 
binsum1 <- summary(bin1)
binsum1
# functions of measures
bin_mean(10,0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)
```















