---
title: "Introduction.Rmd"
author: "Chuyun Guo"
date: "5/1/2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
--- 

```{r,echo=FALSE,message=FALSE}
knitr::opts_chunk$set(collapse = T , comment = "#>")
library(binomial)
library(ggplot2)
```

## Binomial

The package "binomial" is an implementation for calculating probabilities of a Binomial random variable.

## Function bin_choose()

A main function that calculates the number of combinations in which *k* successes can occur in *n* trials.

For instance, the number of combinations in which k = 2 successes can occur in n = 5 trials is
```{r}
bin_choose(5, 2)
```


## Function bin_probability()

A main funtion that take three **valid** arguments *success*, *trials*, and *prob* to come up with the probability of gatting *k* successes in *n* trails with *prob* of success.

For instance, the probability of getting 2 successes in 5 trials, assuming prob of success = 0.5 is
```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)
```

## Function bin_distribution()

A main function that have two arguments *trials*, and *prob*. 
The returned output should be a data.frame with two classes: c("bindis", "data.frame")
The returned output is a data frame with the probability distribution: *sucesses* in the first column, *probability* in the second column.

For instance, data with the probability distribution for 5 trails with a prob of 0.5 is.
```{r}
bin_distribution(trials = 5, prob = 0.5)
```

A plotting method `plot.bindis()` that graphs a barplot to display the probability histogram of a binomial distribution     

```{r}
dis1 <- bin_distribution(trials = 5, prob = 0.5) 
plot(dis1)
```


## Function bin_cumulative()

A main function with two arguments *trials*, and *prob* that return a data frame with both the probability distribution and the cumulative probabilities: *sucesses* in the first column, *probability* in the second column, and *cumulative* in the third column..

For example, 
```{r}
bin_cumulative(trials = 5, prob = 0.5)
```

Function `plot.bincum()` graphs the cumulative distribution

for example, 
```{r}
dis2 <- bin_cumulative(trials = 5, prob = 0.5) 
plot(dis2)
```


## 1.7) Function bin_variable()
A main function that takes two arguments *trials* and *prob* that a binomial random variable object "binvar"

The method function `print.binvar()` is a method function that is able to nicely print the content of the object "binvar"

For example, 
```{r}
bin1 <- bin_variable(trials = 10, p = 0.3) 
bin1
```

The method function `summary.binvar()` is a function that gives full summary description of the object "binvar"

The method function `print.summary.binvar()` can be used to nicely print the contents of an object "summary.binvar"

```{r}
bin1 <- bin_variable(trials = 10, p = 0.3) 
binsum1 <- summary(bin1)
binsum1
```



## Functions of measures

These are main functions that take two arguments: *trials* and *prob* which are used to check the validity of inputs and then do the corresponding calculation.
The calculation includes the mean of a binomial variable, the variance of a binomial variable, the mode of a binomial variable, the skewness of a binomial variable, and the kurtosis of a binomial variable.
For example, 
```{r}
bin_mean(10, 0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)
```





